Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-24 qpip0.tex
Re-indent
Approximately cut qpip0 into 3 theorems

% \begin{proof}
% Step~\ref{step:sum-ob}:
% \begin{align}
%   ( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}_{\regX,\regZ}
%   &= \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}
% \end{align}
% \end{proof}

@@

\begin{theorem}
	\Ethan{First part of main theorem this section}
	$z_i\approx z_{good, i}$
\end{theorem}

\begin{theorem}
	\Ethan{Second part of main theorem this section}
	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
	\Ethan{Need to define $d_i$ here}
\end{theorem}

\begin{theorem}
	\Ethan{TODO some kinda average argument}
\end{theorem}

@@

	For soundness, We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.

	For all $k\leq m$, $d\in \zo^k$, \Ethan{and for all $\gamma$?} and $\ket{\psi} \in H_{\regX,\regZ}$, define

	$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$

	By Lemma~\ref{lem:partition2}, we can decompose
	\begin{align} \label{eq:partition-string}
		\ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
		=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
		=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
		&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}},
	\end{align}

	where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$. %\hannote{Note that the prover's state is actually a mixed state. In particular, $\ket{\psi}$ depends on $pk$ and we are considering the mixed state averaged over the verifier's choice of $pk$.}

@@

	And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$   %\hannote{problem with $e_j$ or $e_i$}

@@

	Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities. Note that $z$ is ``sub-normalized", i.e. $\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.

Define

\begin{align}
	z_{good,i}=\E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
\end{align}

@@

\begin{proof}

@@

@@

Now we try to  put together all $i\in [m]$. Define
$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$

We now proceed to prove that $z_{good}$ is close to the ideal distribution.

@@

%old protocol when jerection on 4-th round
% The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of Protocol~\ref{proto:urmila4} in Protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself. The prover then picks a uniformly random $\gamma$ and  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$. If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead. This is possible because all the inputs are classical.  On the fourth round, there are four possibilities depending on $c$ and whether the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$. If $c=0$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}. If $c=1$ and the prover generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U$ and check whether every copy except the $i$-th copy would be accepted. If all $m-1$ copies accepts, he reply with the $i$-th copy, otherwise reply $\bot$. If $c=0$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he runs $U_{trivial}$ and repies. If $c=1$ and the prover failed to generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he replies with $\bot$. \footnote{Recall that $c=0$ is the testing round and $c=1$ is the Hadamard round.}

@@

\begin{align}
	(d,z_{good,i})\approx_{c, O(\eps)}(d,z_{ideal,i}).
\end{align}

@@

Therefore  we have  
\begin{align}
	(d,z)\approx_{c, O(\eps)}(d,z_{ideal}).
\end{align}
%\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}

>>>>

@@

@@

For soundness, We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
\Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}

For all $k\leq m$, $d\in \zo^k$, $\gamma$ \Ethan{domain for $\gamma$?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$

By Lemma~\ref{lem:partition2}, we can decompose
\begin{align} \label{eq:partition-string}
	\ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
	&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}},
\end{align}
where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

@@

And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$

@@

Define
\begin{align}
	z_{good,i}=\E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
\end{align}

\begin{theorem}
	\Ethan{First part of main theorem this section}
	$z_i\approx z_{good, i}$
\end{theorem}
\begin{proof}

@@

@@

\begin{theorem}
	\Ethan{Second part of main theorem this section}
	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
	\Ethan{Need to define $d_i$ here}
\end{theorem}
\begin{proof}

@@

@@

@@

\begin{align}
	(d,z_{good,i})\approx_{c, O(\eps)}(d,z_{ideal,i}).
\end{align}
\end{proof}

\begin{theorem}
	\Ethan{TODO some kinda average argument}
\end{theorem}
\begin{proof}
Now we try to put together all $i\in [m]$. Define
$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$

We now proceed to prove that $z_{good}$ is close to the ideal distribution.
Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
$$z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities. Note that $z$ is ``sub-normalized", i.e. $\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.

	\Ethan{Here use the 2nd thm}

@@

Therefore  we have  
\begin{align}
	(d,z)\approx_{c, O(\eps)}(d,z_{ideal}).
\end{align}
\end{proof}
